Formalization, Mechanization and Automation of \\ G\"{o}del's Proof of God's Existence

### 2013-10-31 Talks/FU-Berlin/talk-part-6.tex
Add another result
Add slides for criticisms

\begin{frame}{Criticisms}{S5}

@@

\begin{frame}{Criticisms}{Modal Collapse}

@@

\begin{frame}{Criticisms}{No Neutral Properties}

@@

\begin{frame}{Summary of Results for Logic} \small
\begin{itemize}[<+->]
\item Infra-structure for reasoning with modal logic using existing proof assistants and higher-order automated theorem provers
\item A new natural deduction calculus for higher-order modal logic
\end{itemize}
\end{frame}

\begin{frame}[plain]
\includegraphics[width=\textwidth]{TUWien-GodComputerC} 
\end{frame}

>>>>

\begin{frame}{Criticisms}{S5} \centering
$$
\all P.[ \pos \nec P \imp \nec P ] 
$$

\medskip

If something is possibly necessary, then it is necessary.

\pause

\bigskip

$
\pos\only<8->{_c} \nec\only<8->{_c} (A \vee \neg A)
$
\pause
\qquad 
$
\nec\only<8->{_c} (A \vee \neg A)
$

\pause

\bigskip

logical necessity $\sim$ validity
%\qquad\qquad
\hfill
logical possibility $\sim$ satisfiability

\pause

\medskip

$ 
\textrm{for all } M, M \models F 
\quad \longrightarrow \quad
\nec F
%\qquad\qquad\quad
\hfill
\textrm{exists } M, M \models F 
\quad \longrightarrow \quad
\pos F
$

\pause

\bigskip

What about iterations?
$$
\pos \nec \pos \pos F
$$

\medskip

\pause

Weak intuitions $\Rightarrow$ dozens of modal logics

\medskip

\pause

\alert{S5 is considered adequate}

@@

\begin{frame}{Criticisms}{Modal Collapse} \centering
$$
\all P.[ P \imp \nec P ] 
$$

\medskip

Everything that is the case is so necessarily.

\pause

\medskip

Follows from T2, T3 and D2.

\pause

\medskip

There are no contingent ``truths''. \\ \pause
Everything is determined. \\ \pause
There is no free will. \\ \pause
God's existence makes no difference.

\pause
\bigskip

Many proposed solutions: Anderson, Fitting, H\'ajek, \ldots

@@

\begin{frame}{Criticisms}{No Neutral Properties} \centering

$$\all \phi [P(\neg \phi) \biimp \neg P(\phi)]$$

Either a property is positive or its negation is (never both)

\pause
\bigskip

Are the following properties positive or negative?

$$
\lambda x. G(x) \qquad \pause \lambda x. human(x) \qquad \pause \lambda x. foreigner(x) \qquad \lambda x. \neg foreigner(x), \ldots
$$

\pause
\bigskip

Solution: \\
``\ldots positive in the moral aesthetic sense (independently of the accidental structure of the world). Only then the ax. true. [sic] \ldots''
\\ \hfill - G\"odel, 1970
\end{frame}

@@

\begin{frame}{Summary of Results for Logic} \small
\begin{itemize}[<+->]
\item Infra-structure for reasoning with modal logic using existing proof assistants and higher-order automated theorem provers
\item A new natural deduction calculus for higher-order modal logic
\item Difficult benchmarks for higher-order automated theorem provers
\end{itemize}
\end{frame}

\begin{frame}[plain]
\colorbox{black}{\includegraphics[width=\textwidth]{TUWien-GodComputerC}}
\end{frame}
